False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2015-07-23 ms.tex
more work

\usepackage{natbib}
\usepackage{amssymb,amsmath}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage[all]{hypcap}
\renewcommand*{\backref}[1]{[#1]}

@@

\newcommand{\ntotal}{8826}
\newcommand{\nfail}{1584}
\newcommand{\ncalc}{7242}
\newcommand{\nval}{1500}
\newcommand{\nvalnew}{1000}
\newcommand{\nfp}{500}
\newcommand{\nfpnew}{200}
\newcommand{\kepler}{\textit{Kepler}}
\newcommand{\vespa}{\texttt{vespa}}
\newcommand{\isochrones}{\texttt{isochrones}}
\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}

@@

The goal of this work is to calculate the \ac{fpp} for every \ac{koi},
regardless of classification as CONFIRMED, CANDIDATE, or FALSE
POSITIVE.  As such, we begin with a list of \ntotal\ \acp{koi} from
the cumulative table at the \ac{nexsci} Exoplanet Archive.  We then
gather ancillary data and constraints from various sources (described
below) in order to enable the \vespa\ calculation. For various
reasons, the data are not available for every \ac{koi}, and so in the
end we present \ac{fpp} results for \ncalc\ \acp{koi}.

For each \ac{koi} we obtain the following data:
\begin{enumerate}
\item The RA/Dec coordinates of each star from the \ac{kic}.
\item $grizJHK$ photometry from the \ac{kic}, with $griz$ bands
  corrected to the \ac{sdss} photometric scale according to
  \citet{Pinsonneault:2012}.
\item Stellar $T_\mathrm{eff}$, [Fe/H], and $\log g$ values and
  uncertainties from the \citet{Huber:2014} stellar properties
  catalog, if the provenance of these values is from spectroscopy or
  asteroseismology.
\item Detrended \kepler\ photometry used for the \ac{mcmc} modeling of
  \citet{Rowe:2015}, along with information about individually fitted
  transit times, where available.
\item Best-fit $R_p/R_\star$ from the \citet{Rowe:2015} MCMC analysis.
\item Centroid uncertainty information from the \ac{nexsci} Exoplanet
  Archive: we assume that the allowed ``exclusion'' radius for a blend
  scenario is 3$\times$ the uncertainty in the fitted centroid
  position (the \verb|koi_dicco_msky_err| column in the Archive
  table).  We floor this value at 0\farcs5, to prevent unrealistically
  small exclusion radii.
\item The maximum secondary eclipse depth allowed by the
  \kepler\ photometry.  This quantity is obtained from vetting
  metrics produced internally by the \kepler\ Science Office.  When
  these metrics are not available for a particular \ac{koi}, we
  default to 10$\times$ the uncertainty in the \kepler\ pipeline
  measured transit depth (\verb|koi_depth_err1|).

@@

@@

\acrodef{fpp}[FPP]{false positive probability}
\acrodef{koi}[KOI]{\kepler\ Object of Interest}
\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}
\acrodef{kic}[KIC]{Kepler Input Catalog}
\acrodef{sdss}[SDSS]{Sloan Digital Sky Survey}

>>>>

\usepackage{natbib}
\usepackage{amssymb,amsmath}
\usepackage{color}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage[all]{hypcap}
\renewcommand*{\backref}[1]{[#1]}

@@

\newcommand{\ntotal}{8826}
\newcommand{\nfail}{1584}
\newcommand{\ncalc}{7242}
\newcommand{\nval}{1500}
\newcommand{\nvalnew}{1000}
\newcommand{\nfp}{500}
\newcommand{\nfpnew}{200}
\newcommand{\nbadphot}{1009} %EmptyPhotometry or MissingKOI
\newcommand{\nbadphotFP}{897}
\newcommand{\nbadphotCAND}{111}
\newcommand{\nbadrowemcmc}{210}
\newcommand{\nbadstellar}{80} %MissingStellar
\newcommand{\nbadsec}{82} %NoWeakSecondary
\newcommand{\kepler}{\textit{Kepler}}
\newcommand{\vespa}{\texttt{vespa}}
\newcommand{\isochrones}{\texttt{isochrones}}
\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}

%% TODO commands
\newcommand{\todo}[3]{{\color{#2} \emph{#1} TODO: #3}}
\newcommand{\tdmtodo}[1]{\todo{TDM}{red}{#1}}

@@

The goal of this work is to calculate the \ac{fpp} for every \ac{koi},
regardless of classification as CONFIRMED, CANDIDATE, or FALSE
POSITIVE.  As such, we begin with a list of \ntotal\ \acp{koi} from
the cumulative table at the \ac{nexsci} Exoplanet Archive.  We then
gather ancillary data and constraints from various sources in order to
enable the \vespa\ calculation:

\begin{enumerate}
\item The RA/Dec coordinates of each star from the \ac{kic}.
\item $grizJHK$ photometry from the \ac{kic}, with $griz$ bands
  corrected to the \ac{sdss} photometric scale according to
  \citet{Pinsonneault:2012}.
\item Stellar $T_\mathrm{eff}$, [Fe/H], and $\log g$ values and
  uncertainties from the \citet{Huber:2014} stellar properties
  catalog, if the provenance of these values is from spectroscopy or
  asteroseismology.
\item Detrended \kepler\ photometry used for the \ac{mcmc} modeling of
  \citet{Rowe:2015}, along with information about individually fitted
  transit times, where available.  
\item Best-fit $R_p/R_\star$ from the \citet{Rowe:2015} MCMC analysis.
\item Centroid uncertainty information from the \ac{nexsci} Exoplanet
  Archive: we assume that the allowed ``exclusion'' radius for a blend
  scenario is 3$\times$ the uncertainty in the fitted centroid
  position (the \verb|koi_dicco_msky_err| column in the Archive
  table).  We floor this value at 0\farcs5, to prevent unrealistically
  small exclusion radii.
\item The maximum secondary eclipse depth allowed by the
  \kepler\ photometry.  This quantity is obtained from vetting
  metrics produced internally by the \kepler\ Science Office.  When
  these metrics are not available for a particular \ac{koi}, we
  default to 10$\times$ the uncertainty in the \kepler\ pipeline
  measured transit depth (\verb|koi_depth_err1|).  While these
  secondary metrics are not yet available on the Archive, they should
  become available with the final data release.

@@

Of the \ntotal\ total \acp{koi}, \nbadphot\ did not receive \ac{mcmc}
modeling.  Most of these (\nbadphotFP) are already designated FALSE
POSITIVE at the archive, though \nbadphotCAND\ have CANDIDATE
disposition.  One, K00245.04, is a confirmed planet.  \tdmtodo{Find
  out why??}  An additional \nbadrowemcmc\ did receive \ac{mcmc}
modeling but had unphysical fit results; e.g., negative $R_p/R_\star$
or best-fit impact parameter greater than $(1 + R_p/R_\star)$.  Of the
\acp{koi} that did have usable \ac{mcmc} fits, \nbadsec\ had no
\verb|koi_depth_err1| on the archive, and thus had no weak secondary
constraint and were left out of the calculations.  After all these

@@

\acrodef{fpp}[FPP]{false positive probability}
\acrodef{koi}[KOI]{\kepler\ Object of Interest}
\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}
\acrodef{kic}[KIC]{Kepler Input Catalog}
\acrodef{sdss}[SDSS]{Sloan Digital Sky Survey}
\acrodef{ttv}[TTV]{transit timing variations}
